--- 
title: "A Minimal Book Example"
author: "Grégoire Virepinte"
date: "2018-07-24"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is an attempt to prevent me from forgetting everything I have ever learned in Machine Learning."
---

# Introduction {-}

## Why this book? {-}
The basic aim of this book is to collect a few revision cards about Machine Learning. Those are mainly things that I have learned during the past year and forgotten not long after, which really is a shame.

## Why write this in English? {-}
There a few reasons for that:

- I could potentially publish this in the future, one day, which means that I might as well write it in English from the very beginning,

- I have been burned enough times with UTF-8-incompatible encoding (accents missing, that sort of thing), and I don't want that to happen again.

- Most of the Machine Learning vocabulary seems to be in English anyway, and I don't want to have to resort to Frenglish.

- Because I can.

## What to find here? {-}
This should be the basic idea of the book:

- A succint mathematical description of the concepts mentionned in the book,

- A special emphasis on the conditions of application if I can find some, because I always seem to have problems with those,

- An example in R with the proper code and libraries.



# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
